Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-01-20 draft.tex
Update draft, acceptance.py, and references

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
  \item The angular observable ${S_i}$ can be determined
  independently of any other observable ${S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions; in fact,
  one does not even need to be able to explicitly formulate the
  likelihood at all.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?} In many of the
  decays of interest, there are only say dozens\todo{check!} of events recorded.
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
  \item The approximate multivariate Gaussian distribution of $\vecest{S}$
  allows easier and more correct transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \citeneeded\fred{Our fits
    and others'?} or for more precise predictions of optimized
  observables; e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $K \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as \fred{Could add a sketch. It
    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell
    \ell$.}
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\

@@

The determination of a detector's performance to detect signal events
with accurate determination of the event's angles is generally a difficult
task. In the ideal case, one would have an explicit probabilistic model of
the detector acceptance effects and could thus write down the full
forward model from which the measured events arise. In practice, this
would require much more CPU time than available, and one is therefore
forced to simplify the model. The standard approach is to generate
the \emph{true} particle events $\lbrace x_\text{t}^{(n)}\rbrace =
\lbrace(\vec{\nu}^{(n)}_\text{t},\vec\theta^{(n)}_\text{t})\rbrace$, $n=1,\dots,N_\text{t}$, from a PDF
assumed to describe the bare physical process, and to propagate those
particles through a detailed simulation of the detector.
The observable traces that the particles leave in the detector are fed
into reconstruction algorithms resulting in the \emph{detector} events
$\lbrace x^{(n)}_\text{d}\rbrace = \lbrace(\vec{\nu}^{(n)}_\text{d},
\vec\theta^{(n)}_\text{d})\rbrace$, $n=1,\dots,N_\text{d}$.
Most generally, the detected events $\lbrace x_\text{d}^{(k)}\rbrace$
are distributed as $P_\text{d}$,
\begin{equation}
    P_\text{d}(x_\text{d}) = \int P_\text{t}(x_\text{t}) E(x_\text{d}, x_\text{t}) \rmdx{x_\text{t}}\,.
\end{equation}
Here $P$ is the probability distribution of the true events, and the kernel $E(x_\text{d}, x_\text{t})$
parametrizes acceptance and resolution
effects. Note that $P_\text{d}$ is \emph{not} a PDF, since it is not normalized,
\begin{equation}
    \int P_\text{d}(x) \rmdx{x} \neq 1\,.
\end{equation}
For the sake of clarity, we will restrict ourselves
to pure acceptance effects and suppress resolution effects in the remainder of this section; i.e.,
\begin{equation}
    E(x_\text{d}, x_\text{t}) \equiv \eps(x_\text{t}) \delta(x_\text{d}, x_\text{t})\,.
\end{equation}
We will refer to $\eps$ as the \emph{detector acceptance} function. In what follows,
we propose a systematic methods to unfold all effects of $\eps$ through MC simulations
and the method of moments.\\

We will now proceed with the explicit usage of a uniangular PDF with $x = \cos\theta$.\footnote{%
    The generalization of this section to multiangular PDFs is straighforward. It can be achieved
    by promoting $x$ to a vector, promoting the Legendre polynomials to products of independent polynomials
    and the indices $i,j,k,m$ to multi-indices.
}
Let us define the PDF in terms of the Legendre polymials (i.e., $f_k(x) \equiv P_k(x)$),
\begin{equation}
    P(x) \equiv \sum_k S_k f_k(x),
\end{equation}
where $k = 0, 1, \dots$ denotes the total angular momentum of the observables.
From the normalization of the PDF then follows $S_0 = 1/2$. From positivity of $P$ one
obtains $|S_k| \leq 1/2$ for angular momentum $k > 0$. More stringent relations between the
$S_k$ might hold, but are beyond the scope of this work. For latter use, we define
$\vec{S}^{(m)}_k \equiv 1/2 (\delta_{k,0} + \delta_{k,m})$, and we emphasize that
\begin{equation}
    P^{(m)}(x) \equiv P(x | \lbrace S^{(m)}_k \rbrace)
\end{equation}
is a PDF. The dual basis of angular functions follows then from the normalization
and orthogonality of the Legendre polynomials, and one therefore has
\begin{equation}
    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x),\qquad \int_{-1}^{+1} \tilde{f}_k(x) f_l(x) \rmdx{x} = \delta_{k,l}\,.
\end{equation}

@@

@@

In order to study the performance of the proposed method, we simulate
measurements for one uni-angular and one tri-angular decay
distribution for various numbers of events. As inputs we use the SM
predictions for the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to
K\pi)\ell^+\ell^-$, respectively. We cover the $q^2$ ranges $1 \GeV^2$
to $6 \GeV^2$, and $15 \GeV^2$ to the respective kinematic endpoint,
with two bin widths: $1\GeV^2$ and $0.5\GeV^2$. This is to ensure that
a wide spectrum of possible values for
the angular observables.\\

Our finding can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the pull \fred{should define pull} distribution of the observable.
        All pull distributions can successfully be fitted to a gaussian distribution. As an example, we
        show the pull distributions for the observables $S_5$ and $S_7$ for a SM-like $B\to K^*\ell^+\ell^-$
        decays in \reffig{pulls}.
    \item We study the absolute uncertainty $\sigma_k(K)$ with respect to the angular observable $S_k$
        as a function of the number of simulated events $K$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \label{eq:unc-on-mean}
            \sigma_k(K) = \frac{\sigma_k(1)}{\sqrt{K}}
        \end{equation}
        with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
        for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $K$.}
\end{itemize}
We find that all of the above results show consistently that the joint distrbution of the angular observables
converges towards a multivariate Gaussian distribution. We propose to describe the resulting distribution as
a multivariate Gauss when skewness and kurtosis are small enough. The precise targets for these quantities
are subject to the details of the physical analysis, and therefore outside the scope of our work.

@@

\hrulefill\\
{\textbf{\color{red}[dvd: can the following be removed?]}
We used the simulated events and fitted a likelihood function to them.
\begin{itemize}
    \item For a small number of simulated events, \danny{$K=?$}, we observe a significant bias in the pull distributions.
    \item For a large number of simulated events, \danny{$K=?$}, the uncertainty of the angular observables is
        smaller compared to the results of the method of moments.
\end{itemize}
todo: compare robustness to likelihood fit when fit doesn't
converge. Why exactly doesn't it converge? What if physics model
wrong, say some angular terms are missing.}
\hrulefill

@@

Let us assume that the angular decomposition has been achieved for some
PDF $P$ for all except one angle $\theta$. We now focus on only of the resulting
observables $S(\theta) \equiv S(\vec{\nu},\theta)$. The dependence on the non-angular
variables will be dropped in the following. \danny{Fred: is this less confusing now?}
Further, let $S$ have an expansion in terms of partial waves
$l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
\begin{equation}
    \label{eq:def-partial-wave-observable}
    S(\theta) \equiv F\left[A_1(\theta) A_2^*(\theta)\right] \equiv F\left[\left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_2^{*(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\right]\,,
\end{equation}
where $F \in \{\text{Re},\text{Im}\}$ denotes taking either the real
or the imaginary part. Here $p_{l}^{(m)}$ denotes an \emph{associated Legendre} polynomial and $m_i$ is the third component of the angular momentum of the amplitude $A_i$, and we impose $m_1 \geq m_2$.\\

@@

In the last step, we use Gaunt's formula \cite{Gaunt:1929} to integrate a triple product of associated Legendre polynomials,
\begin{equation}
\begin{aligned}
    T_{l_1,l_2,j}^{(m_1,m_2)}
        & = \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta)\\
        & = (-1)^{s - l_1 - m_2} \frac{2 (l_1 + m_1)! (l_2 + m_2)! (2s - 2 l_2)! s!}{(l_1 - m_1)! (s - j)! (s - l_1)! (s - l_2)! (2s + 1)!}\\
        & \times \sum_{t=p}^q (-1)^t \frac{(j + m + t)!(l_1 + l_2 - m - t)!}{t! (j - m - t)! (l_1 - l_2 + m + t)! (l_2 - m_2 - t)!}\,,
\end{aligned}
\end{equation}
where
\begin{equation}
\begin{aligned}
    m & = m_1 + m_2\,, &
    m_1 & \geq m_2\,,  \\
    j, l_1, l_2 & \geq 0\,, &
    m, m_1, m_2 & \geq 0\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
    s & = \frac{j + l_1 + l_2}{2}\,, &
    p & = \max(0, l_2 - l_1 - m)\,, &
    q & = \min(l_1 + l_2 - m, j - m, l_2 - m_2)\,.
\end{aligned}
\end{equation}
The necessary conditions for $T \neq 0$ are
\begin{equation}
    \label{eq:angular-momentum-addition}
    s \in \mathbb{N}\qquad \wedge \qquad l_1 - l_2 \leq l \leq l_1 + l_2,.
\end{equation}
The latter condition is well known from the addition rules of angular momenta. Note, however, that
the sum in \refeq{def-partial-wave-observable} goes to infinitely high angular momenta $l_1$ and $l_2$. As a consequence
of this and of \refeq{angular-momentum-addition}, the angular observables $P_{j,m}$
consist of sums with infinitely many terms. It is then up to theoretical analyses to
estimate or calculate the impact of individual contributions, with or without the cut off $L$.
For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
We close by remarking that for any angular-momentum cut off $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum
of all remaining partial waves through the inclusive decay; i.e., schematically
\begin{equation}
    \sum_{i=1}^2 \sum_{l=L}^\infty |A_i^{(l)}|^2 \leq \frac{\rmdx{^{1 + \dim\vec\nu}} \Gamma_\text{incl}}{\rmdx{\cos\theta} \rmdx{\vec\nu}}\,.
\end{equation}

>>>>

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
  \item The angular observable ${S_i}$ can be determined
  independently of any other observable ${S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions; in fact,
  one does not even need to be able to explicitly formulate the
  likelihood at all.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?} In many of the
  decays of interest, there are only say dozens\todo{check!} of events recorded.
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
  \item The approximate multivariate Gaussian distribution of $\vecest{S}$
  allows easier and more correct transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
    Descotes-Genon:2013wba,Bobeth:2013soa},
  or for more precise predictions of optimized observables; e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $K \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as \fred{Could add a sketch. It
    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell
    \ell$.}
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\

@@

The determination of a detector's performance to detect signal events
with accurate determination of the event's angles is generally a difficult
task. In the ideal case, one would have an explicit probabilistic model of
the detector acceptance effects and could thus write down the full
forward model from which the measured events arise. In practice, this
would require much more CPU time than available, and one is therefore
forced to simplify the model. The standard approach is to generate
the \emph{true} particle events $\lbrace x_\text{t}^{(n)}\rbrace =
\lbrace(\vec{\nu}^{(n)}_\text{t},\vec\theta^{(n)}_\text{t})\rbrace$, $n=1,\dots,N_\text{t}$, from a PDF
assumed to describe the bare physical process, and to propagate those
particles through a detailed simulation of the detector.
The observable traces that the particles leave in the detector are fed
into reconstruction algorithms resulting in the \emph{detector} events
$\lbrace x^{(n)}_\text{d}\rbrace = \lbrace(\vec{\nu}^{(n)}_\text{d},
\vec\theta^{(n)}_\text{d})\rbrace$, $n=1,\dots,N_\text{d}$.
Most generally, the detected events $\lbrace x_\text{d}^{(k)}\rbrace$
are distributed as $P_\text{d}$,
\begin{equation}
    P_\text{d}(x_\text{d}) = \int P_\text{t}(x_\text{t}) E(x_\text{d}, x_\text{t}) \rmdx{x_\text{t}}\,.
\end{equation}
Here $P_\text{t}$ is the probability distribution of the true events, and the kernel $E(x_\text{d}, x_\text{t})$
parametrizes acceptance and resolution
effects. Note that $P_\text{d}$ is \emph{not} a PDF, since it is not normalized,
\begin{equation}
    \int P_\text{d}(x) \rmdx{x} \neq 1\,.
\end{equation}
For the sake of clarity, we will restrict ourselves
to pure acceptance effects and suppress resolution effects in the remainder of this section; i.e.,
\begin{equation}
    E(x_\text{d}, x_\text{t}) \equiv \eps(x_\text{t}) \delta(x_\text{d}, x_\text{t})\,.
\end{equation}
We will refer to $\eps$ as the \emph{detector acceptance} function. In what follows,
we propose a systematic methods to unfold all effects of $\eps$ through MC simulations
and the method of moments.\\

We will now proceed with the explicit usage of a uniangular PDF with $x = \cos\theta$.\footnote{%
    The generalization of this section to multiangular PDFs is straighforward. It can be achieved
    by promoting $x$ to a vector, promoting the Legendre polynomials to products of independent polynomials
    or spherical harmonics, and promoting the indices $i,j,k,m$ to multi-indices.
}
Let us define the PDF in terms of the Legendre polymials (i.e., $f_k(x) \equiv P_k(x)$),
\begin{equation}
    P(x) \equiv \sum_k S_k f_k(x),
\end{equation}
where $k = 0, 1, \dots$ denotes the total angular momentum of the observables.
From the normalization of the PDF then follows $S_0 = 1/2$. From positivity of $P$ one
obtains $|S_k| \leq 1/2$ for angular momentum $k > 0$. More stringent relations between the
$S_k$ might hold, but are beyond the scope of this work. For latter use, we define
$\vec{S}^{(m)}_k \equiv 1/2 (\delta_{k,0} + \delta_{k,m})$, and we emphasize that
\begin{equation}
    P^{(m)}(x) \equiv P(x | \lbrace S^{(m)}_k \rbrace)
\end{equation}
is a PDF. The dual basis of angular functions follows then from the normalization
and orthogonality of the Legendre polynomials, and one therefore has
\begin{equation}
    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x),\qquad \int_{-1}^{+1} \tilde{f}_k(x) f_l(x) \rmdx{x} = \delta_{k,l}\,.
\end{equation}

@@

The accuracy of the unfolding process as outlined above critically depends on both the accuracy
of the detector simulation, as well as the uncertainties induced by the MC estimates. While
considerations of any detector simulation is beyond the scope of this work, we can, however,
comment on the MC-induced uncertainties. As usual, one needs to find a balance between
compute time and accuarcy. We find for a uniangular distribution and a total of $6\cdot 10^6$ MC
samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$) that the error on the mean is
smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that the unfolding
matrix is universal in a sense. Specifically, it can be reused in analyses with a similar underlying decay.
Therefore, computing resources spent on improving its accuracy are therefore not wasted.

@@

We now study the performance of the proposed method. In order to do so, we simulate
individual events for two separate physical processes: one uni-angular, and one tri-angular decay
distribution. We repeats theses analysis for varying sample sizes, ranging from
$50$ to $500$ events. Our toy analysis base on SM predictions for angular observables
in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively.
In order to faithfully investigate the performance of the method of moments, we repeats our
numerical studies for several bin sizes in the kinematic range $1 \GeV^2 \leq q^2 \leq 6\GeV^2$,
as well as $15 \GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin size is chosen either
as $1\GeV^2$ or $0.5\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
values for the angular observables is investigated.\\

Our finding can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the distribution of the $\mathrm{pull}$
        of any observables $S$,
        \begin{equation}
            \mathrm{pull_i} \equiv \frac{\est{S} - S}{\est{\sigma}_S}\,.
        \end{equation}
        Here $S$ refers to the true (input) value for the angular observables, $\est{S}$ refers to the
        MC estimate, and $\est{\sigma} \equiv \sqrt{\est{\Sigma}}$ refers to an estimator of the
        variance of the measurement. All pull distributions obtained in our studies can be successfully
        fitted to a gaussian distribution. Due to the large number of studied distributions, we have
        to restrict ourselved to a subset. In our opinion the pull distributions for the observables
        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
        decays, are good examples. We show their respective pull distributions for \danny{$XXX$} toy studies
        of $200$ events per study in \reffig{pulls}.
    \item We study the absolute uncertainty $\sigma_k(K)$ with respect to the angular observable $S_k$
        as a function of the number of simulated events $K$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \label{eq:unc-on-mean}
            \sigma_k(K) = \frac{\sigma_k(1)}{\sqrt{K}}
        \end{equation}
        with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
        for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $K$.}
\end{itemize}
All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
observables converges towards a multivariate Gaussian distribution. We therefore propose to describe the
resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis, and reside therefore outside the scope of this work.

@@

@@

Let us assume that the angular decomposition has been achieved for some
PDF $P$ for all angles except one, which we label $\theta$. We now focus on only of of the resulting
observables, which we label $S(\theta) \equiv S(\vec{\nu},\theta)$. The dependence on the non-angular
variables will be suppressed in the following. \danny{Fred: is this less confusing now?}
Further, let $S$ have an expansion in terms of partial waves
$l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
\begin{equation}
    \label{eq:def-partial-wave-observable}
    S(\theta) \equiv F\left[A_1(\theta) A_2^*(\theta)\right] \equiv F\left[\left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_2^{*(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\right]\,,
\end{equation}
where $F \in \{\text{Re},\text{Im}\}$ denotes taking either the real
or the imaginary part. Here $p_{l}^{(m)}$ denotes an \emph{associated Legendre} polynomial and $m_i$ is the third component of the angular momentum of the amplitude $A_i$, and we impose $m_1 \geq m_2$.\\

@@

In the last step, we use Gaunt's formula \cite{Gaunt:1929} to integrate a triple product of associated Legendre polynomials,
\begin{equation}
\begin{aligned}
    T_{l_1,l_2,j}^{(m_1,m_2)}
        & = \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta)\\
        & = (-1)^{s - l_1 - m_2} \frac{2 (l_1 + m_1)! (l_2 + m_2)! (2s - 2 l_2)! s!}{(l_1 - m_1)! (s - j)! (s - l_1)! (s - l_2)! (2s + 1)!}\\
        & \times \sum_{t=p}^q (-1)^t \frac{(j + m + t)!(l_1 + l_2 - m - t)!}{t! (j - m - t)! (l_1 - l_2 + m + t)! (l_2 - m_2 - t)!}\,,
\end{aligned}
\end{equation}
where
\begin{equation}
\begin{aligned}
    m & = m_1 + m_2\,, &
    m_1 & \geq m_2\,,  \\
    j, l_1, l_2 & \geq 0\,, &
    m, m_1, m_2 & \geq 0\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
    s & = \frac{j + l_1 + l_2}{2}\,, &
    p & = \max(0, l_2 - l_1 - m)\,, &
    q & = \min(l_1 + l_2 - m, j - m, l_2 - m_2)\,.
\end{aligned}
\end{equation}
The necessary conditions for $T \neq 0$ are
\begin{equation}
    \label{eq:angular-momentum-addition}
    s \in \mathbb{N}\qquad \wedge \qquad l_1 - l_2 \leq l \leq l_1 + l_2,.
\end{equation}
The latter condition is well known from the addition rules of angular momenta. Note, however, that
the sum in \refeq{def-partial-wave-observable} goes to infinitely high angular momenta $l_1$ and $l_2$. As a consequence
of this and of \refeq{angular-momentum-addition}, the angular observables $P_{j,m}$
consist of sums with infinitely many terms. It is then up to theoretical analyses to
estimate or calculate the impact of individual contributions, with or without the cut off $L$.
For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
We close by remarking that for any angular-momentum cut off $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
width.
